\item [3D audio technology] Simulation that creates the illusion of sound sources placed anywhere in 3 dimensional space, including behind, above or below the listener.
\item [ADT] A home security and home automation company commonly known as ADT, which originates from "American District Telegraph". ADT offers professionally installed and monitored home security and automation services to users in a subscription model.
\item[Action-event control] Process where a user action creates an physical event.
\item [API] Application Programming Interface - enables other software to use this applications functionality.
\item [Ausim] 3D audio hardware company.
\item [Automatic beam steering] Signal processing technique to narrow the microphone coverage area. Used to pick out a speaker and suppress background noise coming from directions other than that of the speaker.
\item[Benchmarking] A process of researching and observing to understand the state of the art for a given field or topic.
\item[Bluetooth Smart] A wireless personal area network technology specifically designed for low power consumption and low cost.
\item[Brainstorming] A process by which groups of people generate ideas.
\item [Brainwaves] A common term that refers to post-synaptic potentials measured from many neurons in the brain.
\item [California Duster] A brand of car duster made of many fibers that lift dust from the car’s surface to keep it clean between car washes.
\item [CDR] Center for Design Research at Stanford University.
\item [CEP] Otherwise known as a Critical Experience Prototype, this is a prototype built to test an experience that is critical to addressing the problem statement.
\item [CFP] Otherwise known as a Critical Function Prototype, this is a prototype built to test a (technical) function that is critical to addressing the problem statement.
\item [Client] Computer program that accesses a server.
\item [Client-server paradigm] A computing architecture which separates the client from a server over a computer network. 
\item [Connected device] A device equipped with networking capabilities and connected to a network.
\item [Crowded channel] A communication channel that is clogged with information.
\item [CVE] Acronym for Collaborative Virtual Environment. This is a virtual environment that support more than one user at the same time.
\item [Dark Horse] An idea that is unlike the others preceding it, an outlier.
\item [Fitness tracker wristband] A wristband that carries sensors that measure its wearers vital signals to analyze and reflect upon his activity at day and night.
\item [Home Security System] A network of sensors, cameras, and motion detectors that are wired together to determine if unauthorized intruders are entering a home. The system must be armed and disarmed manually by homeowner using a key pad, or in more advanced systems, a smart phone.
\item [HUD] Head-up display --- information is shown on a drivers windshield, without blocking the sight on what lies behind it.
\item [Interaction model] A general concept for a mapping between digital data and the mental models of a user.
\item [Key Fob Case] A cell phone case that contains the electronics of a key fob along with additional connectivity to connect to the phone and home.
\item [Light Therapy] A special kind of light that is designed to mimic the sun's light spectrum, helping to treat users of SAD (see below).
\item[LGM] Large Group Meeting. The weekly meeting of the local ME310- and SUGAR-teams together with the respective teaching assistants.
\item [Low power mesh networks] A network of computers that are connected without a central hub and that consume very little power while doing this.
\item [Meditation Room] A space that is specifically designed to be peaceful and quiet, allowing people to quietly contemplate and find inner peace.
\item [Near Field Communication (NFC)] Radio communication over very short distances that has become the standard platform for contactless payment platforms such as Apple Pay and Google Wallet.
\item[OBD (adapter)] On-Board Diagnostics. An interface that allows to pull certain statistics and data from a vehicle via an adapter such as speed, error codes and pedal position.
\item[Persona] A fictional person representing identified user needs in order to have a reference user for designing the new product. 
\item [Seasonal Affective Disorder (SAD)] A specific type of major depression brought on by changing of the seasons to include more rain and less sun. SAD is often treated with light therapy, traditional therapy, and medication.
\item[Smart home hub] A wireless router type device made by companies like Wink and SmartThings that connects all smart home devices together. This acts as an access point for the mobile phone to control devices.
\item [Smart Key Fob] An electronic key for the car that unlocks the car via proximity sensors. It does not need to be removed from one's pocket or purse to open the car.
\item [Tokenization] The standard security feature of contactless payment systems that ensures security of data using.
\item [Towel Arm] A bundle of microfiber towel held by plastic tongs.
\item [Waterless Car Wash] A solution marketed as an environmentally car wash replacement using very little liquid. Solution is sprayed on car surface and wiped off with a towel - no other rinsing or drying required.